Observations

### 2020-05-09 exp_eth_val.Rmd
Add files via upload

* Aim:
    + Test the effect of heterogeneous preferences depending on value attribution: circle care more about value neighborhood composition, square care more about ethnic neighborhood composition.
    + This is the case  we discussed, adapting to circle tolerant, square intolerant
    + How preference heterogeneity affects results in  the previous section, where agents hold  same preference
    + How mutual adaptation of circle and square driven by different hierarchy of preference affect each other segregation patterns
    + Interaction of heterogeneous preferences with relative group size for ethnic and value membership
* Assumptions: 
    + square hold higher ethnic than value preferences: $\beta^{\square}_e \geq \beta^{\square}_v$; circle hold higher value than ethnic preferences: $\beta^{\circ}_v \geq \beta^{\circ}_e$.
    + No difference due to ethnic membership
    + \textbf{NOTE: Here only baseline} for question of time/computation server (Tab: \ref{tab:Second}). I'd collect conditions of majority and minority circle or square in ethnic different group sizes.
* Figures
    + Circle orange and square orange is taken as prototype (in the legend circle, square), since any subgroup in Fig: \ref{fig:thheory} has same probability $0.25$ to relocate close similar one and behavior would be symmetrical \textbf{-> agree? I would test otherwise}
    + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
    + Considering the critical levels of $\beta = 5$ between high randomness and low randomness (space model Fig: \ref{fig:baselineone}), I jump here directly to critical points $\beta = 0$: total ranomness,  $\beta = 5$: min determinism, $\beta = 10$: max determinism, this for each dimensions and faceting for circle and value group.
    + ANNEX B heatmaps: ethnic and value segregation for all preferences of square faceted for the 3 critical points of circle (Fig: \ref{fig:heatmapdsquare}); ethinic and value segregation for all preferences of circle faceted for the 3 critical points of square (Fig: \ref{fig:heatmapdcircle})
    + Fig: \ref{fig:betatwoethnic} and Fig: \ref{fig:betatwovalue} compares in the same graph ethnic and value segregation for circle and square agents, narrowing down compared to ANNEX B. Focus: the lower the distance between ethnic and value segregation, the more the agent relocates close to a members of the own ethnic and value subgroup (Fig: \ref{fig:thheory})

@@

```{r betatwoethnic,fig.pos='H',fig.out="96%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value preference square, faceting conditions: preferences of circle", echo=FALSE, include=TRUE }

@@

```{r betatwovalue,  fig.pos="H",fig.out="96%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation between", echo=FALSE, include=TRUE  }

@@

@@

>>>>

* Aim:
    + Test the effect of heterogeneous preferences depending on value attribution: circle care more about value neighborhood composition, square care more about ethnic neighborhood composition.
    + This is the case  we discussed, adapting to circle tolerant, square intolerant
    + How preference heterogeneity affects results in  the previous section, where agents hold  same preference
    + How mutual adaptation of circle and square driven by different hierarchy of preference affect each other segregation patterns
    + Interaction of heterogeneous preferences with relative group size for ethnic and value membership
* Assumptions: 
    + square hold higher ethnic than value preferences: $\beta^{\square}_e \geq \beta^{\square}_v$; circle hold higher value than ethnic preferences: $\beta^{\circ}_v \geq \beta^{\circ}_e$.
    + No difference due to ethnic membership
    + \textbf{NOTE: Here only baseline} for question of time/computation server (Tab: \ref{tab:Second}). I'd collect conditions of majority and minority circle or square in ethnic different group sizes.
* Figures
    + Circle orange and square orange is taken as prototype (in the legend circle, square), since any subgroup in Fig: \ref{fig:thheory} has same probability $0.25$ to relocate close to agents of same ethnicity and same value. Proof in ANNEX B, reporting behavior of circle blue and square blue
    + Need to find trade off between 4 parameters (see Tab: \ref{tab:Second}) and behavior of 2 type of agents (circle and blue) in conditions of relative group size
    + Considering the critical levels of $\beta = 5$ between high randomness and low randomness (space model Fig: \ref{fig:baselineone}), I jump here directly to critical points $\beta = 0$: total ranomness,  $\beta = 5$: min determinism, $\beta = 10$: max determinism, this for each dimensions and faceting for circle and value group.
    + ANNEX B heatmaps: ethnic and value segregation for all preferences of square faceted for the 3 critical points of circle (Fig: \ref{fig:heatmapdsquare}); ethinic and value segregation for all preferences of circle faceted for the 3 critical points of square (Fig: \ref{fig:heatmapdcircle})
    + Fig: \ref{fig:betatwoethnic} and Fig: \ref{fig:betatwovalue} compares in the same graph ethnic and value segregation for circle and square agents, narrowing down compared to ANNEX B. Focus: the lower the distance between ethnic and value segregation, the more the agent relocates close to a members of the own ethnic and value subgroup (Fig: \ref{fig:thheory})

@@

```{r betatwoethnic,fig.pos='H',fig.out="94%",fig.show = "hold",fig.align='center',fig.cap="Difference segregation, x-axis: difference ethnic and value square preference, faceting: circle preference", echo=FALSE, include=TRUE }

@@

```{r betatwovalue,  fig.pos="H",fig.out="94%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Difference segregation, x-axis: difference ethnic and value circle preference, faceting: square preference", echo=FALSE, include=TRUE  }

@@

e_square.labs <- c("ß ethnic \nsquare 0", "ß ethnic \nsquare 5", "ß ethnic \nsquare 10")
names(e_square.labs) <- c("0", "5","10")
v_square.labs <- c("Square ß value 0", "Square ß value 5", "Square ß value 10")
names(v_square.labs) <- c("0", "5","10")

@@

```{r betatwoethnicblue,fig.pos='H',fig.out="94%",fig.show = "hold",fig.align='center',fig.cap="Testing blue: Difference segregation, x-axis: difference ethnic and value square preference, faceting: circle preference", echo=FALSE, include=TRUE }

ibe_10 <- circle_frame %>%  filter(beta_ie_square == 10) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ibe_5 <- circle_frame %>%  filter(beta_ie_square == 5) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square"))) %>%
  ggplot(aes(x = (beta_ie_square - beta_iv_square), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_iv_circle ~  beta_ie_circle, labeller = labeller(rev_beta_iv_circle = rev_beta_iv_circle.labs,  beta_ie_circle = e_circle.labs )) +
  scale_x_discrete(name = "ß ethnic square 10 - ß value square", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ibe_5
ibe_10
```

```{r betatwovalueblue,  fig.pos="H",fig.out="94%",fig.show = "hold", fig.align='center',fig.show="hold", fig.cap="Testing blue: Difference segregation, x-axis: difference ethnic and value circle preference, faceting: square preference", echo=FALSE, include=TRUE  }

ibv_10 <- circle_frame %>%  filter(beta_iv_circle == 10) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  geom_vline(xintercept = 5, color = "red") +
  scale_x_discrete(name = "ß value circle 10 - ß ethnic circle", limits = seq(0,10, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ibv_5 <- circle_frame %>%  filter(beta_iv_circle == 5) %>% gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl,eth_cl_bl,val_cl_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"ethnic segregation" = c("eth_sq_bl","eth_cl_bl"), "value segregation" = c("val_sq_bl","val_cl_bl")), "ethnic segregation"), `group` = fct_relevel(fct_collapse(subgroup, "square" = c("eth_sq_bl","val_sq_bl"), "circle" = c("eth_cl_bl","val_cl_bl"), "square")))  %>%
  ggplot(aes(x = (beta_iv_circle - beta_ie_circle), y = Segra, color = `segregation`, shape = `group`)) + geom_line() + geom_point( size = 2) + facet_grid(rev_beta_ie_square ~  beta_iv_square, labeller = labeller(rev_beta_ie_square = rev_beta_ie_square.labs, beta_iv_square = v_square.labs))  +
  scale_x_discrete(name = "ß value circle 5 - ß ethnic circle", limits = seq(0,5, by = 1)) +  ylab("Segregation") +
  scale_color_manual(values = c("dark violet","dark green"), guide = guide_legend(title="")) +
  scale_shape_manual(values = c(16,15), guide = guide_legend(title="")) +
    theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ibv_5
ibv_10
